Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-04 paper/paper.tex
experimenting...

An \emph{attribute} is a symbol $A$.
The set of all attributes is $\mathcal{A}$.
An \emph{attribute value} is a symbol $a$.
The set of all attribute values is $\Omega$.
An \emph{attribute value space} is a function $\sigma : \mathcal{A} \implies 2^{\Omega}$
specifying the set of valid values that attributes can take on.
A \emph{row} with respect to $\sigma$
is a function $r : \mathcal{A} \implies \Omega$
where $r(A) \in \sigma(A)$.
The set of all rows is $\mathcal{R}$.
A \emph{database} is a tuple $\db =
\tuple{
    \mathcal{A}_{\db},
    \Omega_{\db},
    \sigma_{\db},
    \mathcal{R}_{\db}
}$
where
$\mathcal{A}_{\db} \subseteq \mathcal{A}$
is the set of attributes in $\db$,
$\Omega_{\db} \subseteq \Omega$
is the set of attribute values in $\db$,
$\sigma_{\db} : \mathcal{A}_{\db} \implies 2^{\Omega_{\db}}$
is the function specifying the valid values that each attribute can take on in $\db$,
and $\mathcal{R}_{\db} \subseteq \mathcal{R}$
is the set of rows in $\db$
with $r_\db : \mathcal{A}_\db \implies \Omega_\db$
for all $r_\db \in \mathcal{R}_\db$
and $r_\db(A) \in \sigma_\db(A)$
for all $A \in \mathcal{A}_\db$.
The set of all databases is $\dbs$.

@@

As for privacy, on the other hand, it introduces risks of information leakage. Releasings of real data may inadvertently reveal sensitive information by data inference attacks.

TODO: ppl may infer info from auditors analyses Releasings. repeated queries

Indefinite retention also exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.

@@

% this 100 experiment is not run yet

With heuristic it is 924m15s. The fit time is 17m1s without heuristic.

@@

With heuristic it is 27m33s. The fit time is 33s without heuristic.

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.0787.}
\label{tab:compas_score}
\begin{tabular}{cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
\midrule
Demographic Parity  & 0.1310 & 0.0980 & 0.0330 \\
Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 \\
Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 \\
Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 \\
Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 \\
Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 \\
\bottomrule
\end{tabular}
\end{table}

@@

% this is running with 100 iter

@@

The average of their differences is $0.0069$. Without heuristic it is $0.0083$.

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is 0.0069.}
\label{tab:diabetes_score}
\begin{tabular}{cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
\midrule
Demographic Parity  & 0.0135 & 0.0032 & 0.0102 \\
Mean Difference     & 0.0035 & 0.0119 & 0.0083 \\
Accuracy Eqaulity   & 0.0077 & 0.0009 & 0.0067 \\
Equalized Odds 1    & 0.0000 & 0.0003 & 0.0003 \\
Equalized Odds 2    & 0.0086 & 0.0104 & 0.0017 \\
Accuracy Equality 1 & 0.0133 & 0.0095 & 0.0038 \\
Accuracy Equality 2 & 0.0216 & 0.0039 & 0.0177 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

An \emph{attribute} is a symbol $A$.
The set of all attributes is $\mathcal{A}$.
An \emph{attribute value} is a symbol $a$.
The set of all attribute values is $\Omega$.
An \emph{attribute value space} is a function $\sigma : \mathcal{A} \implies 2^{\Omega}$
specifying the set of valid values that attributes can take on.
A \emph{row} with respect to $\sigma$
is a function $r : \mathcal{A} \implies \Omega$
where $r(A) \in \sigma(A)$.
The set of all rows is $\mathcal{R}$.
A \emph{database} is a tuple $\db =
\tuple{
    \mathcal{A}_{\db},
    \Omega_{\db},
    \sigma_{\db},
    \mathcal{R}_{\db}
}$
where
$\mathcal{A}_{\db} \subseteq \mathcal{A}$
is the set of attributes in $\db$,
$\Omega_{\db} \subseteq \Omega$
is the set of attribute values in $\db$,
$\sigma_{\db} : \mathcal{A}_{\db} \implies 2^{\Omega_{\db}}$
is the function specifying the valid values that each attribute can take on in $\db$,
and $\mathcal{R}_{\db} \subseteq \mathcal{R}$
is the set of rows with respect to $\sigma_{\db}$ in $\db$
with $r_\db : \mathcal{A}_\db \implies \Omega_\db$
for all $r_\db \in \mathcal{R}_\db$
and $r_\db(A) \in \sigma_\db(A)$
for all $A \in \mathcal{A}_\db$.
The set of all databases is $\dbs$.

@@

As for privacy, on the other hand, it introduces risks of information leakage. Releasings of analyses on real data may inadvertently reveal sensitive information by data inference attacks. Attackers can exploit patterns in data outputs or combine outputs with external data to infer sensitive information.

@@

% this 100 experiment is running

The fit time is 17m1s without heuristic. With heuristic it is 924m15s.

@@

The fit time is 33s without heuristic. With heuristic it is 27m33s.

The average of their differences is $0.0750$. Without heuristic it is $0.0727$.

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is $0.0750$. Average of differences without heuristic is $0.0727$}
\label{tab:compas_score}
\begin{tabular}{cccccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
\midrule
Demographic Parity  & 0.1310 & 0.0980 & 0.0330 & 0.0809 & 0.0501 \\
Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 & 0.0146 & 0.0067 \\
Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 & 0.0802 & 0.0553 \\
Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 & 0.0825 & 0.0648 \\
Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 & 0.0551 & 0.1157 \\
Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 & 0.0256 & 0.1439 \\
\bottomrule
\end{tabular}
\end{table}

@@

@@

The average of their differences is $0.0067$. Without heuristic it is $0.0078$.

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is $0.0067$. Average of differences without heuristic is $0.0078$}
\label{tab:diabetes_score}
\begin{tabular}{cccccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
\midrule
Demographic Parity  & 0.0135 & 0.0038 & 0.0096 & 0.0015 & 0.0119 \\
Accuracy Eqaulity   & 0.0077 & 0.0011 & 0.0065 & 0.0011 & 0.0065 \\
Equalized Odds 1    & 0.0000 & 0.0006 & 0.0006 & 0.0010 & 0.0010 \\
Equalized Odds 2    & 0.0086 & 0.0106 & 0.0020 & 0.0094 & 0.0008 \\
Accuracy Equality 1 & 0.0133 & 0.0090 & 0.0042 & 0.0059 & 0.0074 \\
Accuracy Equality 2 & 0.0216 & 0.0041 & 0.0175 & 0.0019 & 0.0197 \\
\bottomrule
\end{tabular}
\end{table}
